A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-25 main.tex
Yabaizo...

$\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
$\text{mulmat}$ takes two integer which are the size of multiplicand matrix and generate a code.
The last integer to decide the size of multiplier matrix is given at runtime.
You can generate a code by applying two integers to $\text{mulmat}$.
We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
\QPercent\ states that we can erase this $\%_\alpha$ under some conditions.

@@

% Describe "some conditions".

\begin{definition}[Values]
	$A \neq \epsilon$\\
	\begin{align*}
		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon)                           & \\
		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
	\end{align*}

	% Valueの説明

\end{definition}

>>>>

$\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
$\text{mulmat}$ takes two integer which are the size of multiplicand matrix and generate a code.
The last integer to decide the size of multiplier matrix is given at runtime.
You can generate a code by applying two integers to $\text{mulmat}$.
We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
\QPercent\ states that we can erase this $\%_\alpha$ under a conditions which is explained in the next paragraph.

The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.

@@

At the end of definition section, we define values, a staged reduction, and evaluation contexts of \LMD.

\begin{definition}[Values]
	$A \neq \epsilon$\\
	\begin{align*}
		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon)                           & \\
		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
	\end{align*}
\end{definition}
